I would like to thank my advisor, Roberto Ierusalimschy, for his patience as I
searched for my research topic, for his trust in my work, and for the
revision of the text. Working with Roberto gave me the assurance that my work
was held to high standards at all moments.

I thank the members of the Examination Committee, professors Renato Cerqueira,
Raquel Prates, Hermann Haeusler and Simone Barbosa for their review and for
their encouraging comments. I also thank Simone for giving me early pointers
that ended up influencing greatly the resulting work.

I am thankful to all my friends at LabLua, who made this lab a second (or
perhaps first) home for me during these five years. Especially, I would like
to thank Ana Lúcia, for running the lab, being a delight to work with
throughout our projects, but most of all for the support and advice
in many crucial moments. Thank you for not letting me give up on my vision.

I thank the friends I made in Rio (some of whom aren't here anymore), who made
these years here so much better, and to the ones from the South (some of whom
aren't there anymore), who always made me feel like the years hadn't passed
whenever I went to visit. The bonds we make along the way are the most
precious thing in life, and I am fortunate to have made strong ones that the
distance did not and will not break, no matter where life takes us.

Finally, my deepest gratitude goes to my family, who always cheered me on from
the distance and who are always there for me, and in particular to my lovely
girlfriend Patrícia, for her support, encouragement, and for keeping me moving
forward. Your tenacity is inspiring; you are an example I try to follow.

\bigskip 

This work was partly supported by CNPq and PUC-Rio, and for that I
am grateful.
