%% -*- coding: utf-8; -*-

\documentclass[
  phd,
  %% master
  %% brazilian
  american
]{ThesisPUC}


%%%
%%% Additional Packages
%%%

  %% \usepackage[brazilian]{babel}      %% in ThesisPUC.cls
  %% \usepackage[utf8]{inputenc}        %% .
  %% \usepackage[T1]{fontenc}           %% .
  %% \usepackage{lmodern}               %% .
  %% \usepackage[pdftex]{graphicx}	%% .

  \usepackage{tabularx}
  \usepackage{multirow}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage[%
    dvipsnames,
    svgnames,
    x11names,
    fixpdftex
  ]{xcolor}
  \usepackage{numprint}
  \usepackage{textcomp}
  \usepackage{booktabs}
  \usepackage{amsmath}
  \usepackage{enumitem}
  \usepackage{amssymb}
  \usepackage{textcomp}
% \usepackage{etoolbox}

% LyX comments --Hisham
\usepackage{comment}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{rotfloat}

% Interpreter preambles --Hisham
\input{PdInterpreter_preamble.tex}
\input{XlInterpreter_preamble.tex}
\input{LvInterpreter_preamble.tex}

%% numprint 
\npthousandsep{.}
\npdecimalsign{,}

%% ThesisPUC option
%% \tablesmode{figtab} %% [nada, fig, tab ou figtab]

% ============
% Bibliography
% ============

\usepackage[numbers]{natbib}
\bibliographystyle{alpha}
  
% Numerar o capítulo da bibliografia --Hugo
% See http://tex.stackexchange.com/a/116785/45056
\AtBeginDocument{%
    \renewcommand{\bibsection}{\chapter{\bibname}}
}


%%%
%%% Counters
%%%

%% uncomment and change for other depth values
%% \setcounter{tocdepth}{3}
%% \setcounter{lofdepth}{3}
%% \setcounter{lotdepth}{3}
%% \setcounter{secnumdepth}{3}


%%%
%%% New commands and other global definitions
%%%

% \input{defs}


%%%
%%% Misc.
%%%

\usecolour{true}


%%%
%%% Titulos
%%%

\author{Hisham Hashem Muhammad}
\authorR{Hashem Muhammad, Hisham}

\advisor{Roberto Ierusalimschy}{Prof.}
\advisorR{Ierusalimschy, Roberto}

%% \title{Desenvolvimento de um sistema de microscopia digital para
%%  classificação automática de tipos de hematita em minério de ferro}

\title{Semânticas de dataflow para aplicações programáveis por usuários finais}

\titleuk{Dataflow Semantics for End-user Programmable Applications}

\day{28}
\month{April}
\year{2017}

\city{Rio de Janeiro}
\CDD{004}
\department{Informática}
\program{Informática}
\school{Centro Técnico Científico}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC--Rio}


%%%
%%% Jury
%%%

\jury{%
  \jurymember{Renato Fontoura de Gusmão Cerqueira}{Prof.}
    {IBM Research - Brazil}{}
  \jurymember{Raquel Oliveira Prates}{Profª.}
    {Departamento de Ciência da Computação}{UFMG}
  \jurymember{Edward Hermann Haeusler}{Prof.}
    {Departamento de Informática}{PUC-Rio}
  \jurymember{Simone Diniz Junqueira Barbosa}{Profª.}
    {Departamento de Informática}{PUC-Rio}
  \schoolhead{Márcio da Silveira Carvalho}{Prof.}
}


%%%
%%% Resume
%%%

\resume{%
The author graduated in Computer Science from Universidade do Vale
do Rio dos Sinos --- Unisinos in 2002, and obtained the degree of Mestre at
Pontifícia Universidade Católica do Rio de Janeiro --- PUC-Rio in 2006.
He obtained the degree of Doutor at PUC-Rio in 2017,
where he worked in the field of programming languages.
}


%%%
%%% Acknowledgment
%%%

\acknowledgment{%
\input{ack.tex}
}


%%%
%%% Catalog prekeywords
%%%

\catalogprekeywords{%
  \catalogprekey{Engenharia Química}%
  \catalogprekey{Engenharia de Materiais}%
}


%%%
%%% Keywords
%%%

\keywords{%
  \key{Linguages de Programação;}
  \key{Semântica;}
  \key{Dataflow;}
  \key{Programação por Usuários Finais.}
}

\keywordsuk{%
  \key{Programming Languages;}%
  \key{Semantics;}%
  \key{Dataflow;}%
  \key{End-User Programming.}%
}


%%%
%%% Abstract
%%%

\abstract{%
\input{resumo.tex}
}

\abstractuk{%
\input{abstract.tex}
}


%%%
%%% Dedication
%%%

\dedication{%
  To my mother and father,\\
who never used computers.
}

%%%
%%% Epigraph
%%%

\epigraph{%
  Every generation has to fight the same battles,\\
  for there is no final victory\\
  and there is no final defeat.
}
\epigraphauthor{Tony Benn}
\epigraphbook{(1925 -- 2014)}

%%%
%%% 
%%%

\begin{document}

  % \input{abrevs}
  \input{chapter-1}
  \input{chapter-2}
  \input{chapter-3}
  \input{chapter-4}
  \input{chapter-5}
  \input{chapter-6}
  \input{chapter-7}
  \input{chapter-8}
  \input{chapter-9}
  %% ...
  \arial
  \bibliography{thesis}
  \normalfont
  \input{appendix}

\end{document}
